A thermodynamic view of dusty protoplanetary disks

### 2017-06-12 linear.tex

>>>>

In a future work we will perform a detailed comparison between the
simplified one-fluid and full two-fluid frameworks in calculating SI.

\begin{figure}
\includegraphics[width=\linewidth]{figures/si_2f_1f_compare}
\caption{{\bf in case the paper isn't long enough} Comparison of the linear
streaming instability obtained from a full two-fluid analysis and the current 
one-fluid framework simplified by the terminal velocity approximation. The vertical
wavenumber is fixed and growth rates are maximized over $K_x$. 
\label{si_compare_full}}
\end{figure}
%"generalized stokes number" would include other problem parameters,
%e.g. wavenumber
